### 2019-05-25 doc/chapters/towards_verifying.tex
fixed grammer

  sealed abstract class Satoshis extends CurrencyUnit
\end{lstlisting}
Thus, when we use generics, Satoshis is not of type CurrencyUnit anymore and neither of type CurrencyUnit[A], where A is the new generic type.
Satoshis extends CurrencyUnit with type Int64, so it is of type CurrencyUnit[Int64].
That's to specific.

Since there is no easy way to fix it and the code should stay as much as possible the original, we decided to remove the abstract type.
The verification is a bit more limited, to only Satoshis, but that's no problem, because the goal is to verify the addition of Satoshis.

>>>>

  sealed abstract class Satoshis extends CurrencyUnit
\end{lstlisting}
Thus, changeing it to generics, Satoshis is not of type CurrencyUnit anymore and neither of type CurrencyUnit[A], where A is the new generic type.
Satoshis extends CurrencyUnit with type Int64, so it is of type CurrencyUnit[Int64].
That's to specific.

Since there is no easy way to fix it and the code should stay as much as possible the original, removing the abstract type might be the only choice.
The verification is a bit more limited, to only Satoshis, but that's no problem, because the goal is to verify the addition of Satoshis.
